FraCaS: Temporal Analysis

### 2020-06-03 paper2020/paper.tex
changes

\section{Conclusions and Future Work}
Stergios
\section*{Acknowledgements}

>>>>

\section{Conclusions and Future Work}
We have presented a first attempt for a computational approach dealing with the temporal section of the FraCaS test suite. This is the first time a system is ran against this section, at the same time, this concludes our work in handling the whole of the FraCaS test suite using a combination of a number of well-studied tools: type theory, Grammatical Framework, Monadic Dynamic Semantics and proof assistant technology (Coq). 
\section*{Acknowledgements}
